---
title: "Piloting Graph Learning in Adults"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
```{r}
suppressMessages(library(summarytools, quietly = TRUE))
suppressMessages(library(dplyr, quietly = TRUE))
logdir='~/Dropbox/projects/in_progress/network_learning/code/netlearn_kids_v1/logs/'
datadir='~/Dropbox/projects/in_progress/network_learning/code/netlearn_kids_v1/subjData/'
```

We started out running adults with exposure walks of ~200-300 trials, but in service of having it be doable for kids, iterated down to 150 trials. Here we examine only data from adults run on a version of the task with 150 trials of exposure (NL004 and onwards). Each subject has either the OMOT or the Dyadic Choice task.

At NL008, made the change for tapping on the monsters to advance, tap as quickly as you can, the tap makes a sound, and string all assessments together rather than opening each separately.

## NL004

```{r}
exposureData <- read.delim(paste0(logdir, "NL004/NL004_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "NL004/seqcmpl/NL004_log_seqcmpl.csv"))
#omotData<- read.csv(paste0(datadir, "NL004/OMOT/NL004_log_omot.csv"))
dyadData <- read.csv(paste0(datadir, "NL004/dyad_choice/NL004_log_dyad_choice.csv"))
seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(0,1), labels=c("Incorrect", "Correct"))
#omotData$correct <- factor(omotData$correct, ordered=TRUE, labels=c("Incorrect", "Correct")) #commented out because if make them factors then can't do proportion calculations on them.
```

### Exposure data

What does reaction time on the exposure walk look like?
```{r}
view(dfSummary(exposureData))
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt, main= "RT by Trial Number")
cor.test(exposureData$TrialNumber, exposureData$rt)
```

It goes down (not surprisingly)!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
No, it's not.

**How long does it take with 150 nodes?**
```{r}
max(exposureData$onset)/60
```
### Sequence Completion Task

```{r}
table(seqcmplData$correct)
```
How many are correct (within rather than between community)? 100%

### Dyadic Choice
```{r}
mean(dyadData$correct)
```
77% correct on Dyadic Choice.

Does average number correct differ by trial type?
```{r}
dyadData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
Does the average number they say are friends (yes answers) differ by trial type?

Haven't done this here.

**Does RT differ by trial type?**
```{r}
dyadData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Yes! RT is longer in friends-between trials than friends-within, as expected. RT is longest in what should be the hardest trials (non-friends between distance 2 and non-friends within)

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(dyadData$TrialNumber, dyadData$rt)
```
No, RT goes down with more trials.

### Conclusions

Did better than expected! 100% accuracy on sequence completion and 78% accuracy on dyadic choice.
RT on OMOT looks as we might expect, lowest for conservative trials, highest on catch trials.
Took 9 min with 150 nodes when not told to press as fast as you can.
RT is not longer on transition nodes (4 to 5 or 5 to 4).

## NL005

```{r}
exposureData <- read.delim(paste0(logdir, "NL005/NL005_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "NL005/seqcmpl/NL005_log_seqcmpl.csv"))
omotData<- read.csv(paste0(datadir, "NL005/OMOT/NL005_log_omot.csv"))
#dyadData <- read.csv(paste0(datadir, "NL004/dyad_choice/NL004_log_dyad_choice.csv"))
seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(0,1), labels=c("Incorrect", "Correct"))
#omotData$correct <- factor(omotData$correct, ordered=TRUE, labels=c("Incorrect", "Correct")) #commented out because if make them factors then can't do proportion calculations on them.
```
### Exposure data

What does reaction time on the exposure walk look like?
```{r}
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt, main= "RT by Trial Number")
cor.test(exposureData$TrialNumber, exposureData$rt)
```

It goes down (not surprisingly)!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Yes, by a lot!

**How long does it take with 150 nodes?**
```{r}
max(exposureData$onset)/60
```
### Sequence Completion Task

```{r}
table(seqcmplData$correct)
```
How many are correct (within rather than between community)? 100%

### Odd Man Out Task
```{r}
summary(omotData$correct)
```
On average, 78% correct on OMOT.

Does average number correct differ by trial type?
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
The 'correct' answer for catch trials is the node that is 2 edges away rather than one edge away. 72% is still above chance on the non-conservative trials!

**Does RT differ by trial type?**
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Average RT is lowest in conservative trials, as we would expect, since these should be the easiest!

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(omotData$TrialNumber, omotData$rt)
```
Not significantly.

### Conclusions

Did better than expected! 100% accuracy on sequence completion and 78% accuracy on OMOT.
RT on OMOT looks as we might expect, lowest for conservative trials, accuracy also highest for conservative trials and lowest for catch trials.
Took 12 min with 150 nodes when not told to press as fast as you can.
RT is not longer on transition nodes (4 to 5 or 5 to 4).

## NL006
```{r}
exposureData <- read.delim(paste0(logdir, "NL006/NL006_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "NL006/seqcmpl/NL006_log_seqcmpl.csv"))
#omotData<- read.csv(paste0(datadir, "NL006/OMOT/NL006_log_omot.csv"))
dyadData <- read.csv(paste0(datadir, "NL006/dyad_choice/NL006_log_dyad_choice.csv"))
seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(0,1), labels=c("Incorrect", "Correct"))
#omotData$correct <- factor(omotData$correct, ordered=TRUE, labels=c("Incorrect", "Correct")) #commented out because if make them factors then can't do proportion calculations on them.
```
### Exposure data

What does reaction time on the exposure walk look like?
```{r}
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt, main= "RT by Trial Number")
cor.test(exposureData$TrialNumber, exposureData$rt)
```

It goes down (not surprisingly)!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Yes!

**How long does it take with 150 nodes?**
```{r}
max(exposureData$onset)/60
```
### Sequence Completion Task

```{r}
table(seqcmplData$correct)
```
How many are correct (within rather than between community)? 88%

### Dyadic Choice
```{r}
mean(dyadData$correct)
```
58% correct on Dyadic Choice.

Does average number correct differ by trial type?
```{r}
dyadData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
Does the average number they say are friends (yes answers) differ by trial type?

Haven't done this yet.

**Does RT differ by trial type?**
```{r}
dyadData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Yes! RT is longest in non-friends within and non-friends between with a short distance.

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(dyadData$TrialNumber, dyadData$rt)
```
No it does not.

### Conclusions

88% accuracy on sequence completion and 58% accuracy on dyadic choice.
Took 9 min with 150 nodes when not told to press as fast as you can.
RT is longer on transition nodes (4 to 5 or 5 to 4).


## NL007

```{r}
exposureData <- read.delim(paste0(logdir, "NL007/NL007_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "NL007/seqcmpl/NL007_log_seqcmpl.csv"))
omotData<- read.csv(paste0(datadir, "NL007/OMOT/NL007_log_omot.csv"))
#dyadData <- read.csv(paste0(datadir, "NL004/dyad_choice/NL004_log_dyad_choice.csv"))
seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(0,1), labels=c("Incorrect", "Correct"))
#omotData$correct <- factor(omotData$correct, ordered=TRUE, labels=c("Incorrect", "Correct")) #commented out because if make them factors then can't do proportion calculations on them.
```
### Exposure data

What does reaction time on the exposure walk look like?
```{r}
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt, main= "RT by Trial Number")
cor.test(exposureData$TrialNumber, exposureData$rt)
```

It goes down (not surprisingly)!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Not really.

**How long does it take with 150 nodes?**
```{r}
max(exposureData$onset)/60
```
### Sequence Completion Task

```{r}
table(seqcmplData$correct)
```
How many are correct (within rather than between community)? 62%

### Odd Man Out Task
```{r}
summary(omotData$correct)
```
On average, 75% correct on OMOT.

Does average number correct differ by trial type?
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
The 'correct' answer for catch trials is the node that is 2 edges away rather than one edge away. 44% is still above chance on the non-conservative trials!

**Does RT differ by trial type?**
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Average RT is lowest in conservative trials, as we would expect, since these should be the easiest! Non-conservative is highest.

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(omotData$TrialNumber, omotData$rt)
```
Not significantly, but gets slightly faster.

### Conclusions

62% accuracy on sequence completion and 75% accuracy on OMOT.
RT on OMOT looks as we might expect, lowest for conservative trials, accuracy also highest for conservative trials.
Took 13 min with 150 nodes when not told to press as fast as you can.
RT is not longer on transition nodes (4 to 5 or 5 to 4).

## NL008

NL008 only finished the sequence completion task, did not do dyadic choice or OMOT due to an error in the code.
Here, we changed the protocol to be better for kids such that participants had to tap on the monsters, which then made a sound, and do it as fast as they can.

```{r}
exposureData <- read.delim(paste0(logdir, "NL008/NL008_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "NL008/seqcmpl/NL008_log_seqcmpl.csv"))
seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(0,1), labels=c("Incorrect", "Correct"))
```
### Exposure data

What does reaction time on the exposure walk look like?
```{r}
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt, main= "RT by Trial Number")
cor.test(exposureData$TrialNumber, exposureData$rt)
```

It goes down a lot!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Average is, but not really.

**How long does it take with 150 nodes?**
```{r}
max(exposureData$onset)/60
```
7.5 minutes, still long!
### Sequence Completion Task

```{r}
table(seqcmplData$correct)
```
How many are correct (within rather than between community)? 75%

### Conclusions

75% accuracy on sequence completion.
RT on OMOT looks as we might expect, lowest for conservative trials, accuracy also highest for conservative trials.
Took 7.5 min with 150 nodes when pressing as fast as they can on an alien.
RT is only a little longer on transition nodes (4 to 5 or 5 to 4).
