---
title: "Piloting Graph Learning in Adults"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---
```{r}
library(summarytools, quietly = TRUE)
library(dplyr, quietly = TRUE)
logdir='~/Dropbox/projects/in_progress/network_learning/code/netlearn_kids_v1/logs/'
datadir='~/Dropbox/projects/in_progress/network_learning/code/netlearn_kids_v1/subjData/'
exposureData <- read.delim(paste0(logdir, "NL001/NL001_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "NL001/seqcmpl/NL001_log_seqcmpl.csv"))
omotData<- read.csv(paste0(datadir, "NL001/OMOT/NL001_log_omot.csv"))
seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, labels=c("Incorrect", "Correct"))
```

We started out running adults with exposure walks of ~200-300 trials, but in service of having it be doable for kids, iterated down to 150 trials. Here we examine only data from adults run on a version of the task with 150 trials of exposure (NL004 and onwards).

At NL008, made the change for tapping on the monsters to advance, tap as quickly as you can, and string all assessments together rather than opening each separately.
## NL004

```{r}
view(dfSummary(exposureData))
view(dfSummary(seqcmplData))
view(dfSummary(omotData))
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt)
cor.test(exposureData$TrialNumber, exposureData$rt)
```
It goes down (not surprisingly)!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
No, in fact it's shorter--but in this participant, their first 2 trials were on a transition node. Wonder if that influences things?

**How long does it take with 300 nodes (of which 4 are practice trials)?**
```{r}
max(exposureData$onset)/60
```
## Sequence Completion Task

How many are correct? 75%.
```{r}
table(seqcmplData$correct)
```

## Odd Man Out Task
```{r}
view(dfSummary(omotData))
```
On average, 89% correct on OMOT.

Does average number correct differ by trial type?
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
The 'correct' answer for catch trials is the node that is 2 edges away rather than one edge away. 72% is still above chance on the conservative trials!

**Does RT differ by trial type?**
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Average RT is highest in catch trials, lowest in conservative trials, as we would expect. Median RT is highest in non-conservative trials and lowest in conservative trials, again as we would expect.

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(omotData$TrialNumber, omotData$rt)
```
Yes, it's negative, meaning that RT got faster as they went on.

## Conclusions

Did better than expected--100% accuracy on OMOT conservative and catch trials, 75% accuracy on sequence completion and 72% on non-conservative OMOT trials.
RT on OMOT looks as we might expect, lowest for conservative trials, higher on non-conservative or catch trials.
Took 27 min with 300 nodes.
RT is not shorter on transition node (4 to 5)

# Subject 2

```{r}
exposureData <- read.delim(paste0(logdir, "NL002/NL002_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "NL002/seqcmpl/NL002_log_seqcmpl.csv"))
omotData<- read.csv(paste0(datadir, "NL002/OMOT/NL002_log_omot.csv"))
#seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(1,0), labels=c("Incorrect", "Correct"))
#omotData$correct <- factor(omotData$correct, ordered=TRUE, labels=c("Incorrect", "Correct")) #commented out because if make them factors then can't do proportion calculations on them.
```

## Check exposure data quality

```{r}
view(dfSummary(exposureData))
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt)
cor.test(exposureData$TrialNumber, exposureData$rt)
```
It goes down (not surprisingly)!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Yes, it is!

**How long does it take with 200 nodes?**
```{r}
max(exposureData$onset)/60
```
## Sequence Completion Task
Data quality
```{r}
view(dfSummary(seqcmplData))
```
How many are correct? 100%
```{r}
table(seqcmplData$correct)
```
## Odd Man Out Task
```{r}
view(dfSummary(omotData))
```
On average, 58% correct on OMOT.

Does average number correct differ by trial type?
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
The 'correct' answer for catch trials is the node that is 2 edges away rather than one edge away, but they are within the same community. 44% is still above chance on the non-conservative trials!

**Does RT differ by trial type?**
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Average and median RT is highest in non-conservative trials, lowest in conservative trials, as we would expect.

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(omotData$TrialNumber, omotData$rt)
```
Not strongly so.

## Conclusions

Did better than expected on sequence completion--100% accuracy on sequence completion. 
75% accuracy on OMOT catch trials, 61% on conservative trials and 44% on non-conservative trials (still above chance at 33%),
RT on OMOT looks as we might expect, lowest for conservative trials, highest on non-conservative trials.
Took 13 min with 200 nodes. Should I make it shorter, still?
RT is longer on transition nodes (4 to 5 or 5 to 4).

# Subject 3

```{r}
exposureData <- read.delim(paste0(logdir, "NL004/NL004_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "NL004/seqcmpl/NL004_log_seqcmpl.csv"))
#omotData<- read.csv(paste0(datadir, "NL006/OMOT/NL006_log_omot.csv"))
#seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(1,0), labels=c("Incorrect", "Correct"))
#omotData$correct <- factor(omotData$correct, ordered=TRUE, labels=c("Incorrect", "Correct")) #commented out because if make them factors then can't do proportion calculations on them.
```

## Check exposure data quality

```{r}
view(dfSummary(exposureData))
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt, main= "Sample Adult")
cor.test(exposureData$TrialNumber, exposureData$rt)
```
It goes down (not surprisingly)!
**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
No, it's not.

**How long does it take with 200 nodes?**
```{r}
max(exposureData$onset)/60
```
## Sequence Completion Task
Data quality
```{r}
view(dfSummary(seqcmplData))
```
How many are correct? 88%.
```{r}
table(seqcmplData$correct)
```
## Odd Man Out Task
```{r}
view(dfSummary(omotData))
```
100% correct on OMOT!

Does average number correct differ by trial type?
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
NO difference.

**Does RT differ by trial type?**
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Average and median RT is highest in catch trials, lowest in conservative trials.

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(omotData$TrialNumber, omotData$rt)
```
Not strongly so.

## Conclusions

Did better than expected! 88% accuracy on sequence completion and 100% accuracy on the OMOT.
RT on OMOT looks as we might expect, lowest for conservative trials, highest on catch trials.
Took 17 min with 200 nodes. Not enough variance?
RT is not longer on transition nodes (4 to 5 or 5 to 4).